\documentclass[11pt,a4paper,twoside]{moderncv}

% moderncv themes
\moderncvtheme[blue]{coverletter} 

% character encoding
\usepackage[utf8]{inputenc}     % replace by the encoding you are using
\usepackage{hyperref}
\usepackage{newcent}
\usepackage{verbatim}
\usepackage{setspace}

% adjust the page margins
\usepackage[scale=0.75]{geometry}
\AtBeginDocument{\recomputelengths} % required when changes are made to page layout lengths

% personal data
\firstname{Eduardo}
\familyname{Ballesteros}
\address{Erbprinzen Str.}{75175 Pforzheim GERMANY}    % optional, remove the line if not wanted
\mobile{00 49 (0) 176 3760 6564}
\email{eballes@gmail.com}   % optional, remove the line if not wanted

\nopagenumbers{} % uncomment to suppress automatic page numbering for CVs longer than one page

% offer data
\newcommand{\position}{Software Engineer for INTEGRAL} % position
\newcommand{\company}{ESA/ESAC} % company
%\newcommand{\pollo}{To Whom It May Concern} % Or dear Susi
\newcommand{\pollo}{Dear Karina,}
\newcommand{\companyAddress}{ }

\onehalfspacing
\setlength{\parindent}{0.7cm}
\setlength{\parskip}{2ex plus 0.5ex minus 0.2ex}

\fontfamily{\familydefault}
\selectfont


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------

\begin{document}
\maketitle

\noindent \today \\[1em]

%\noindent \companyAddress \\[1em]

\noindent \pollo

I am writing to express my interest in the {\position} position at {\company}, 
because I am passionate about the space sector and the software development
process. As software engineer, I have worked in the space industry deepening
my understanding in a broad range of roles and positions, from development 
to test, managing requirements as well as performing integration tasks. 

From my education I have learned to develop effective software, flexible and adaptable 
and to be a goal-oriented engineer. My work experiences demostrate that I have a 
well-rounded understanding of the challeges that are faced between different companies 
and in multicultural teams inside the european space industry. I would bring
to your team my enthusiasm for software quality and control, pragmatic problem
solving skills and a drive to always produce the best quality of work for your
company.

I am enclosing my resume to provide you with better understanding
of my experience. You will find that I am well suited for the position and
will make a strong contribution to your company. Please contact me by email at
\url{eballes@gmail.com} if you need any additional information. It would
be my pleasure to meet with you soon. Until then, thank you for your time and
consideration.\\[1.4ex]

\noindent Sincerely yours,

\noindent Eduardo Ballesteros\\[1.0ex]

\noindent Enclosure: Resume
\end{document}
