\documentclass[11pt,a4paper,twoside]{moderncv}

% moderncv themes
%\moderncvtheme[blue]{casual} 
\moderncvtheme[blue]{classic}   % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic} % idem

% character encoding
\usepackage[utf8]{inputenc}     % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.81]{geometry}
%\setlength{\hintscolumnwidth}{3cm} % if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{10cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths} % required when changes are made to page layout lengths

% personal data
\firstname{Eduardo}
\familyname{Ballesteros}
%\title{Software Test Developer}                      % optional, remove the line if not wanted
\address{Erbprinzen Str.}{75175 Pforzheim GERMANY}    % optional, remove the line if not wanted
\mobile{00 49 (0) 176 3760 6564}
\phone{00 34 646 09 22 94}  % optional, remove the line if not wanted
\email{eballes@gmail.com}   % optional, remove the line if not wanted

\nopagenumbers{} % uncomment to suppress automatic page numbering for CVs longer than one page

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------

\begin{document}
\maketitle

\section{Education}
\cventry{2002--2008}{Computer Science Engineer (MSc)}{Technical University of Madrid (UPM)}{Spain} {}{} % arguments 3 to 6 are optionals
\cventry{2007--2008}{Computer Science}{University of Glasgow}{Scotland}{(Exchange student - Erasmus)}{}  

\section{Experience}
\cventry{Aug'10--Present}{Validation Test Engineer}{Thales Alenia Space Deutschland}{Pforzheim}{Germany}{}
\cvlistitem{Working on behalf of GMV as OSPF element specialist and consultant.}
\cvlistitem{Responsible for the integration and validation of the processing chain (OSPF, IPF, MGF) in the GMS.}
\cvlistitem{Designed test procedures and managed requirements in the frame of the GMS.}
\cvlistitem{Developed tools for data analysis and test automation purposes.}
\cventry{Jan'09--Aug'10}{Software Developer}{GMV Aerospace}{Madrid}{Spain}{}
\cvlistitem{Lead the design and development of our unattended OSPF test automation framework.}
\cvlistitem{Developed an environment simulator to test the algorithm facility of OSPF in an isolated environment.}
\cvlistitem{Designed and implemented the Software Integration Plan of the OSPF-RTMC subcomponent.}
\cvlistitem{Implemented test data analysis for the Analysis Tool to verify algorithm results.}
\cvlistitem{Analyzed execution problems and collaborated closely with the development team to correct software bugs.}
%\cvlistitem{Selected to teach a 3h Perl course to fellow co-workers focused on best practices, Perl idioms and code maintainability.}

\cventry{Jul'08-Jan'09\\Sept'06-Sept'07}{Intern at Teldat}{Technical University of Madrid (UPM)}{Spain}{}{}
\cvlistitem{Ported the Java desktop client application to manage the system to a web application using GWT.}
\cvlistitem{Participated in a full development cycle experience, using SCRUM as management methodology, 
for the development of a image capture and distributed communications software system.}
%\cvlistitem{Updated the software and system's database access for a more efficient approach through nested database procedures.}
\cvlistitem{Lead the migration of the error-prone date and time management system to a more maintainable interface using the Joda-Time library.}

\section{Language skills}
\cvcomputer{English}{\textbf{Fluent}}{Spanish}{\textbf{Native}}
%\cvlanguage{English}{Fluent}{}
%\cvlanguage{Spanish}{Native}{}

\section{Computer skills}
\cvcomputer{Languages}{\textbf{Perl}, \textbf{C}, Java, C++, Ada, Haskell}{Tools}{\textbf{DOORS}, CPAN, Valgrind, vim}
\cvcomputer{Others}{MySQL, PL/SQL, Hibernate, \LaTeX}{OS}{Linux, LynxOS}

\end{document}
